03 - Analyses coding

### 2022-06-12 scripts/r/03-analyses-coding.Rmd
♻️ - edit analyses coding; add plots

>>>>

```{r}
coding %>%
  drop_na(outcome, operationalisation) %>%
  filter(
    outcome %in% c("duration", "f0", "intensity"),
    temporal_window %in% c("segment", "word", "phrase", "sentence")
  ) %>%
  droplevels() %>%
  ggplot() +
  geom_mosaic(aes(x = product(outcome, operationalisation), fill = outcome))
```

```{r}
coding %>%
  select(framework:operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
  distinct()
```

```{r}
coding %>%
  select(team, n_models) %>%
  distinct() %>%
  drop_na() %>%
  summarise(mean(n_models), median(n_models), sd(n_models), min(n_models), max(n_models))
```
